Figures to insert in text

### 2018-04-11 Chapters/Chapter01.tex
Hathor: simulations results (only images)

@@

In Bitcoin, it is usually required 6 confirmations before accepting a transaction. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks. Therefore, in order to have the same level of security as Bitcoin, a transaction is said to be confirmed when its accumulated weight is greater than or equal to $\log_2(\mathbf{E}(Y_6) \cdot H) = \log_2(60 \cdot 60 \cdot H) = 4 + \log_2(225) + \log_2(H)$, where $H$ is calculated as the total hash rate of the miners plus the total hash rate of new transactions.

@@

The methodology we have been using is computer simulation. Through the simulation of many scenarios of DAG model with different parameters, we will understand how the network behaves in complex scenarios, mainly when the load is suddenly increased, and when the network is under attack. We will first test our hypothesis through simulation and than prove them mathematically.

@@

When a new transaction is added to the DAG, it uses a depth-first search \citep{cormen2009introduction} (i) to update the aggregated weight of the directly and indirectly confirmed transactions, (ii) to calculate its own score, and (iii) to generate a topological sort \citep{cormen2009introduction}. The topological sort is used to calculate the longest path from all other transactions to the new transaction, and this longest path is used to update the depth of the whole DAG. If the new transaction confirms only transactions which has already been confirmed, the depth update is skipped thanks to Theorem \ref{theorem-new-tx-not-tip}.

The necessary time to generate the proof-of-work is estimated by the function $k \cdot 2^{weight}$, where $k$ is a constant related to the computing power of the agent and weight is randomly chosen.

The time between two new transactions is sampled from the exponential distribution with parameter $\lambda$. The value of $\lambda$ is changed over time, causing changes in the load of the network. We consider 1 tx/s to be a low load, and 15 tx/s to be a high load. Even though we have already tested up to 100 tx/s.

@@

The DAG Model's mining starts just like Bitcoin's, i.e., $\mathbf{P}(h(x) < A) = \frac{A}{2^{256}}$. Then, it follows that solving a transaction proof-of-work follows a geometric distribution. Let $X$ be the number of attempts until a success, then $\mathbf{P}(X=k) = (1-p)^{k-1}p$, where $p=\frac{A}{2^{256}}$. Also, $\mathbf{P}(X \leq k)=1-(1-p)^k$. The average number of attempts is $\mathbf{E}(X)=1/p$.

Let $w$ be the transaction's weight, i.e., $\mathbf{E}(X)=w \Rightarrow w = 1/p$. Let $T = X/H$ be the time required to solve the transaction's proof-of-work, where $H$ is the hash rate of the transaction's owner. Then, $\mathbf{P}(T < t) = \mathbf{P}(X < tH) = 1 - (1 - p)^{tH} = 1 - \left( 1 - \frac{1}{w} \right)^{tH} = 1 - e^{tH \log\left(1 - \frac{1}{w} \right)}$, i.e., $T$ follows an exponential distribution with $\lambda = -H \log\left(1 - \frac{1}{w} \right)$.

% https://math.stackexchange.com/questions/635443/sum-of-exponential-random-variable-with-different-means

@@

Every time a new transaction emerges, it chooses two tips to confirm before solving the proof-of-work. When it finishes solving the proof-of-work, it is propagated and becomes a tip. So, two new transactions may choose the same tips to confirm. If there are $t$ tips, a new transaction will randomly choose 2 out of these $t$ tips, even if they have already been chosen by other new transactions --- in fact, they do not know which have been chosen because these new transactions have not being propagated yet.

The following theorems will be mathematically proved. They have already been used in the implementation of the simulator.

>>>>

\section{Transaction confirmation}

@@

In Bitcoin, it is usually required 6 confirmations before accepting a transaction. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks. Therefore, in order to have the same level of security as Bitcoin, a transaction is said to be confirmed when its accumulated weight is greater than or equal to $\log_2(\mathbf{E}(Y_6) \cdot H) = \log_2(6 \cdot 128 \cdot H) = 7 + \log_2(6) + \log_2(H)$, where $H$ is calculated as the total hash rate of the miners plus the total hash rate of new transactions.

@@

The methodology we have used is computer simulation. Through the simulation of many scenarios of Hathor, we will understand how the network behaves in complex scenarios, including when the load suddenly increases, and when the network is under attack.

@@

When a new transaction emerges, it chooses two tips to confirm before solving the proof-of-work. When it finishes solving the proof-of-work, it is propagated and becomes a tip. So, two new transactions may choose the same tips to confirm. If there are $t$ tips, a new transaction will randomly choose 2 out of these $t$ tips, even if they have already been chosen by other new transactions --- in fact, they do not know which have been chosen because these new transactions have not being propagated yet.

When a new transaction is added to the Hathor's network, it uses a depth-first search \citep{cormen2009introduction} (i) to update the aggregated weight of the directly and indirectly confirmed transactions, (ii) to calculate its own score, and (iii) to generate a topological sort \citep{cormen2009introduction}. The topological sort is used to calculate the longest path from all other transactions to the new transaction, and this longest path is used to update the depth of the whole DAG. If the new transaction confirms only transactions which has already been confirmed, the depth update is skipped thanks to Theorem \ref{theorem-new-tx-not-tip}.

The amount of time spent to solve the proof-of-work is a sample from an exponential distribution.

The time between two new transactions is sampled from an exponential distribution with parameter $\lambda$. The value of $\lambda$ is changed over time, causing changes in the load of the network. We consider 1 tx/s to be a low load, and 15 tx/s to be a high load. Even though we have already tested up to 100 tx/s.

@@

@@
